Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-10 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:10	10:16:14	(Mon10.Aug)

As will be demonstrated in upcoming sections, the LCA beamformer works very well with windows generated from the Kaiser-Bessel function. It is defined as:
%
\begin{align}
w_m = \begin{cases}
\frac{I_0\left(\pi\beta\sqrt{1-\left(\frac{m}{M/2}\right)^2}\right)}{I_0(\pi\beta)}, & 0\le |m|\le M/2 \\
0 & \text{otherwise}
\end{cases}
\end{align}
%
where $I_0$ is the zeroth order Modified Bessel function of the first kind, defined as:
%
\begin{align}
I_0(x) = \sumb{k=0}{\infty} \left[ \frac{\left(\frac{x}{2}\right)^k}{k!} \right].
\end{align}
%

>>>>

As will be demonstrated in upcoming sections, the LCA beamformer works very well with windows generated from the Kaiser-Bessel function. It is defined as:
%
\begin{align}
w_m = \begin{cases}
\frac{I_0\left(\pi\beta\sqrt{1-\left(\frac{2m}{M-1}-1\right)^2}\right)}{I_0(\pi\beta)}, & 0\le m\le M-1 \\
0 & \text{otherwise}
\end{cases}
\end{align}
%
where $I_0$ is the zeroth order Modified Bessel function of the first kind, defined as:
%
\begin{align}
I_0(x) = \sumb{k=0}{\infty} \left[ \frac{\left(\frac{x}{2}\right)^k}{k!} \right]^2.
\end{align}
%
The Kaiser-Bessel window is near optimal in the sense of having its peak energy concentration around $\theta=0$(degrees), for a given time-bandwidth product specified with the parameter $\beta$, defined as 
%
\begin{align}
\beta = \frac{TB}{2},
\end{align}
%
where $T$ is the extent of the window and $B$ is its bandwidth. $\beta$ adjusts the trade-off between mainlobe width and sidelobe level. At small values the windows approach the response of a rectangular window, and at large values ($>5$) the window converges to a Gaussian both in time and frequency.

 adjusts This results in
